\thispagestyle{empty}

In the Standard Model of particle physics the $Z$ boson can decay into a pair of leptons with the same flavour. The observation of the Z boson decaying into a pair of leptons with different flavour, namely the decay into a pair of electron/muon, electron/$\tau$ lepton or muon/$\tau$ lepton would violate lepton flavour conservation and would indicate physical processes beyond the Standard Model. \\

Previous searches for lepton flavour violation in Z boson decays set a constraint on the branching ratio on these decays. For the decay into an electron/muon pair the CMS collaboration set the limit to $\text{BR}(Z\to e\mu) < 7.3\cdot 10^{-7}$, for the decay into a pair of electron/$\tau$ lepton and muon/$\tau$ lepton the LEP collaboration set to limit to $\text{BR}(Z\to e\tau) < 9.8\cdot 10^{-6}$ and $\text{BR}(Z\to \mu\tau) < 1.2\cdot 10^{-5}$. \\

In this analysis the data recorded by the CMS detector in 2016 with a center-of-mass energy of $\sqrt{s} = 13$ TeV and a integrated luminosity of $\mathcal{L} = 35.9$ fb$^{-1}$ is analyzed. All three decays channel are analyzed independently in a model independent approach. In the analysis hadronic decaying $\tau$ leptons are considered. For each final state a boosted decision classifier is trained as discriminating variable. With the CL$_s$ method this classifier is analyzed in bins of jet multiplicity to set expected limits on the branching ratios of the lepton flavour violating Z boson decays. The expected limits are set to $\text{BR}(Z\to e\mu) < 2.8\cdot 10^{-7}$,  $\text{BR}(Z\to e\tau) < 2.25\cdot 10^{-5}$ and  $\text{BR}(Z\to \mu\tau) < 8.6\cdot 10^{-6}$. In comparison to the previous analysis, in the $e\mu$ final state this analysis gained a factor three in terms of sensitivity, in the $e\tau$/$\mu\tau$ final state this analysis is as sensitive as the previous analysis from LEP.
